Survival Set Connectivity

### 2015-05-06 draft.tex
added examples and finish drafting racketrees

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}

\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}

@@

\begin{definition}
A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup E$ such that
\begin{align}
\text{map}(V_t) &\subset V \\
\text{map}(E_t) &\subset E
\end{align}
In other words, vertices map to vertices and edges map to edges. We will usually refer to an embedding as $(T, y, \text{map})$. 
\end{definition}

[ Give some pictures of  tree embeddings here ]

@@

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}

\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}

@@

\begin{definition}
A tree embedding of a weighted graph $G = (V, E)$ will be a tree $T = (V_T, E_T)$ with weights $y: E \rightarrow \mathbb{R}$ and a function $\text{map} : V_T \cup E_t \rightarrow V \cup P(E)$ ($P(E)$ is the power set of $E$) such that
\begin{align}
\text{map}(V_t) &\subset V \\
\text{map}(E_t) &\subset E
\end{align}
In other words, vertices map to vertices and edges map to edges. We will usually refer to an embedding as $(T, y, \text{map})$. 
\end{definition}

@@

We will use a particular type of tree embedding which will allow us to paths in the tree to paths in the graph.

\begin{definition}
For a given graph $G = (V, E)$, a Racke Tree is a tree embedding of $G$, $(T, y, \text{map})$ such that:
\begin{enumerate}
\item $\text{map}$ restricted to the leafs of $T$ is a bijection with the vertices of $G$.
\item For each edge $e \in E_t$ joining $u$ and $v$, $\text{map}(e)$ is a path joining nodes $\text{map}(u)$ and $\text{map}(v)$.
\item For some edge $e \in E_t$, $y_e$ (the cost of the edge) is a special quantity. Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$. Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
\begin{align}
y_e &= \sum_{e' \in \delta(S)} x_e
\end{align}
\end{enumerate}
\end{definition}

\begin{figure}
\centering
\label{fig:rackecut}
\includegraphics[width=0.5\linewidth]{Rackecut.pdf}
\caption{Racke tree cut induced by an edge in the tree.}
\end{figure}

Having made these definition, we can refer to the inverse $\text{map}^{-1}$ in the obvious manner. $\text{map}^{-1}$ on a vertex will map to the corresponding leaf, and $\text{map}^{-1}$ on an edge in the graph will map to all edges in the tree whose paths contain that edge.

\begin{definition}
Given a Racke tree, the load on an edge of the graph $e \in E$ is
\begin{align}
load(e) &= \sum_{f \in \text{map}^{-1}} y_f
\end{align}
The relative load, $rload(e) = \dfrac{load(e)}{x_e}$. 
\end{definition}

Figure~\ref{fig:racketree} gives an example of a Racke tree with the mapping. Each red vertex of the tree is mapped to another red vertex on the graph, and the edge between them corresponds to a path between the red vertices. This gives us a simple way to map flows from Racke trees to the graph and vice-versa.

In particular, if we have a multicommodity flow $\{ f_i \}$ on the graph, then we can easily map into a multicommodity flow on the Racke tree. If there is a flow $f_i$ from $s_i$ to $t_i$, then we find leaves $s_i^{T}=\text{map}^{-1}(s_i)$ and $t_i^T\text{map}^{-1}(t_i)$ and route $f_i$ units of flow through the unique path from $s_i$ to $t_i$.

For obtaining a flow on the graph given one on the Racke tree, if $f_i^T(e)$ is the flow of commodity $i$ on the tree on $e \in E_t$, then we route $f_i^T(e)$ units of flow down the path given by $\text{map}(e)$.

\begin{figure}
\label{fig:racketree}
\centering
\includegraphics[width=\linewidth]{Rackeembeddinggraph.pdf}
\caption{Example Racke Tree where red nodes are mapped and edge maps to a path.}
\end{figure}

There are some crucial properties of Racke trees which we will treat as black boxes. We will define these as lemmas without proof, and we refer to [CITE] for the proofs.

\begin{lemma}
If we have a graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$ and a Racke tree $(T, y, \text{map})$. A multicommodity flow on $G$, $\{ f_i \}$, maps directly to a multicommodity flow on the tree which is also feasible. Likewise, a multicommodity flow on $T$ maps directly into a multicommodity flow on the graph, with the small caveat that we must multiply the capacity of the edge by the relative load. 
\end{lemma}

[ EXPLAIN HOW TO MAP FLOWS ]

\begin{lemma}
For some given graph $G = (V, E)$ and capacities $x: E \rightarrow \mathbb{R}$, we can sample efficiently from Racke trees of $G$, such that 
\begin{align}
\max_{e \in E} \textbf{E}[rload(e)] &\leq \alpha = O(\log n) 
\end{align}
\end{lemma}

\begin{lemma}
The height of the trees sampled is $O(\log nC)$, where $C$ is the ratio of the largest to smallest capacity in $G$. In our cases, the height will always be $O(\log n)$. 
\end{lemma}
